Model for Porous Silicon Structures with a Lateral Gradient

### 2020-10-30 paper.tex
Review introduction to the end

\section{Introduction}
\label{sec:introduction}
Surfaces with a gradient in the refractive index (GRIN) are of
importance as they allow the engineering and tuning of the optical
phase along their surface, yielding applications such as flat
lenses. Furtheremore, there are important biological applications
which combine topographical features with index of refraction
gradients \cite{pierscionek2012gradient}. Preparation of structures
with gradients in other properties have also shown their
usefulness. \notaL{I believe the examples below are unrelated to GRIN,
  thats why I added this remark.} As an example, the
roughness dependent  response of cells has been tested on
materials used applications in medical implants
\cite{bai2020bioinspired}.
Gradients have also been employed for several
technological applications such as high-yield screening of catalysts,
sensing materials and biomolecules \cite{maier2007combinatorial, jayaraman2004construction,
potyrailo2008combinatorial}
Apart from some methods developed by S.E. Fosdick et al \cite{fosdick2010two},
%[JACS  2010, 132, 9226-9227],
synthesis of  Ag-Au alloy gradients on steel and chemical composition
gradients of CdS layers
on gold electrodes have been obtained made by Shannon’s
group\cite{wang2019fabrication}. \notaL{Is this Shannon a big shot, or
  why should we name him?}
Among electrochemical methods, compositional and doping density changes
in  conducting polymers have been used to produce gradients using Indium Tin
Oxide electrodes \cite{inagi2010bipolar}
Electrochemically induced potential gradients have been shown to catalyze the
reactions and gradient doping of polymers \cite{qin2020bipolar, ishiguro2011gradient}.
As compared to the above mentioned techniques, a relatively economical,
fast and easy approach for the fabrication
of gradient materials has been the use  of asymmetrical
electrode configurations in the electrochemical synthesis of porous silicon \cite{sailor2012porous}.
This technique has the additional advantage of being compatible
with VLSI devices and integrable with microelectronics.

Although porous silicon initially stimulated the interest of the scientific
community due to visible PL at room temperature, presently it has
been accepted as a multifaceted optical material due to its large surface
area, biocompatibility, ease of fabrication and tunable refractive index.
Porous silicon emanating applications now cover various fields such as
chemical and biosensor \cite{kumar2020porous},
%[Porous Silicon Fabry–Pérot Interferometer for
%N-Acetyl-β-d-Glucosaminidase Biomarker Monitoring  D. Nanda Kumar,
%Nofar Pinker, and Giorgi Shtenberg  ACS Sensors 2020 5 (7), 1969-1976; DOI:
%10.1021/acssensors.0c00348],
microelectronics and MEMS \cite{martinez2016dual},as well as a
range of optical \cite{estevez2014porous} and optoelectronic applications
\cite{ramadan2020fabrication}. Specifically,
the temporal variation of current density results in the variation of
porosity along the depth for the easy fabrication of different kinds
\cite{perez2018reflectivity} of 1D photonics crystals.
Although the conventional fabrication of PS requires laterally
homogeneous samples (with same structural characteristics on the
porous surface), asymmetric configuration to produce porous silicon
with a lateral gradient (in terms of optical thickness/ pore size and thickness
of the porous layer) has also been exploited for different applications
\cite{collins2002determining}. In this configuration, a small platinum electrode (cathode)
is positioned perpendicular  to the surface of the Si substrate (anode)
at one end or the center  of the cell, resulting  in a decrease in current
density  with an increase in the distance from the electrode
 \cite{khung2008using, clements2011mesenchymal}.
The resulting porous surface can have pore sizes ranging from a few nanometers
to  few micrometers  \cite{wang2015screening}. The range of the dimensions of the pores and
the corresponding  thickness obtained on the same chip can be controlled by
adjusting the location of the pin/circular electrode,  anodizing current density
and etching time period for a given silicon wafer.   Sailor Group
in 2002 \cite{collins2002determining, sailor2012porous} applied it
for the determination of protein size.
Additionally, due to the biocompatible nature of PS, possible gating of
the optical response by variation in pH of the solution was shown to
trap/release the biomolecule for possible drug delivery applications.
 Similar asymmetric electrode configuration was used to fabricate
 optical filters (multilayered structures) with lateral gradient \cite{li2005painting}
% [Li, Yang Yang, Peter Kim, and Michael J. Sailor.
% "Painting a rainbow on silicon–a simple method to
% generate a porous silicon band filter gradient.
% " physica status solidi (a) 202.8 (2005): 1616-1618.]
for developing ethanol sensor (Sailor 2012)\cite{sailor2012porous}.
 Additionally it has been shown that the combination of thermal  oxidation  and
 infiltration of TiO2  by ALD offers the  opportunity to manufacture
a high refractive indices contrast in visibly transparent GRIN
optical elements from PS \cite{ocier2017tunable}.
Kruger et al showed the \cite{krueger2016porous}
%the ...  [ Krueger, Neil A., et al. "Porous silicon gradient
%refractive index micro-optics." Nano letters 16.12 (2016): 7402-7407.]
In addition the same group \cite{krueger2018electrochemical} used porous silicon 1D GRIN structure infiltrated with polymer to synthesize flat microns arrays.

%[Krueger, Neil A., et al.
% "Electrochemical Fabrication of Flat, Polymer‐Embedded
%Porous Silicon 1D Gradient Refractive Index Microlens
%Arrays." physica status solidi (a) 215.13 (2018): 1800088].
Recently, J Wang et al. has shown the fabrication of
miniature spectrometer with PS based rugate filter using
radial interfacial potential distribution \cite{wang2019fabrication}
%(Wang, Joanna,
%Michael J. Sailor, and Byoung‐Yong Chang. "Fabrication of a lateral
%gradient rugate in porous silicon for a miniature spectrometer
%application." ChemElectroChem 6.24 (2019): 5967-5972.
On the other hand, the effect of different topographical
features present on the same chip, has also been
used to culture / adhesion of certain cells \cite{khung2008using}
In the investigation of such practically applicable systems,
the spacial predictability of electrochemical gradients can
be useful for predesigning the devices for different applications.
In this work, we report a simple analytical model to quantitatively
analyze the gradient (calculate the porosity /current density and
thickness) at any point of the GRIN structure.  The paper is organized
as follows. In Section 2  we report a simple analytical model to calculate
the current density/porosity and thickness  at any point of the GRIN structure.
The model contemplates (Dr. Mochan) the formation of electrochemically generated
porous surface  (applicable/extendible to photonic crystals with lateral gradient)
with lateral gradient in refractive index  ...with predictable  depth and porosity
at any point on surface.   In Section 3 we provide experimental details for the
synthesis of porous silicon samples with lateral refractive index gradient.
Section 4 includes experimental results and its comparison with numerically
evaluated parameters. Finally,  the conclusions are given in Section 5
%$
%

%\notaV{ $Painting a rainbow on silicon - A simple method to  generate a porous silicon
%band filter gradient. / Li, Yang Yang; Kim, Peter; Sailor, Michael J.
%In: Physica Status Solidi (A) Applications and Materials Science,
%Vol. 202, No. 8, 06.2005, p. 1616-1618.  (https://doi.org/10.1002/pssa.200461200)
%
%Electrochemical Preparation of Pore Wall Modification Gradients
%across Thin Porous Silicon Layers
%Corrina M. Thompson, Michel Nieuwoudt, Anne M. Ruminski,
%Michael J. Sailor, and Gordon M. Miskelly
%Langmuir 2010 26 (10), 7598-7603
%DOI: 10.1021/la904408h
%
% Richardson, Kathleen A., et al. "Advances in infrared gradient
% refractive index (GRIN) materials: a review." Optical Engineering 59.11 (2020): 112602.
%
%
%Lavanant, Enora, et al. "Radial gradient refractive index
%(GRIN) infrared lens based on spatially resolved crystallization
%of chalcogenide glass." Optical Materials Express 10.4 (2020): 860-867.
%While widely used in the visible, radial gradient refractive
%index (GRIN) lenses are still elusive in the IR waveband.
%In this paper we introduce a new method based on spatially
%resolved crystallization of chalcogenide glass to produce such lenses.
%Optical and structural
%
%Yoon, Sun Mi, et al. "Subwavelength Hollow-Nanopillared Glass
%with Gradient Refractive Index for Ultralow Diffuse Reflectance
%and Antifogging." ACS applied materials & interfaces 12.5 (2020): 6234-6242.
%Nanostructured glass with subwavelength hollow nanopillars
%of diameters of sub-65 nm was fabricated, showing high optical
%transmittance and ultralow diffuse reflectance. A simple
%process involving single-step plasma etching was used on a
%glass slide coated with a SiO2...
%
%Perez, Julius C., Tahmid H. Talukdar, and Judson D. Ryckman.
%"Patterning Refractive Index on the Surface of a Chip by Direct
%Nanoimprinting." CLEO: QELS_Fundamental Science. Optical Society of America, 2020.
%
%Szymanowski, Hieronim, et al. "Thin SiNC/SiOC Coatings with a
%Gradient of Refractive Index Deposited from Organosilicon Precursor." Coatings 10.8 (2020): 794.
%
%Perez, Julius C., Tahmid H. Talukdar, and Judson D. Ryckman.
% "Patterning Refractive Index on the Surface of a Chip by Direct
% Nanoimprinting." CLEO: QELS_Fundamental Science. Optical Society of America, 2020.
% $
%}

@@

This problem may be solved readily using image charge theory \cite{jackson1999classical}.

@@

\section{Conclusions}
\label{sec:conclusion}
By choosing a simple geometry for our electrochemical cell, namely, a
rectangular prism, and employing a point-like electrode, we were able
to derive an expression for the calculation of the electric current
density along the surface of a Si sample. The expression was obtained
by using image charge theory and a planewise summation of Coulomb
potentials in 2D reciprocal space, and it is made up of
a rapidly converging sum of analytical terms, just a few of which
should be kept. This allows the characterization
of the porosity of a PS layer and the etching
rate for different values of the etching current density by making
optical measurements on several positions of just a
few samples. We illustrated the procedure with three samples on each of which we
measured reflectance spectra at eight different positions.
Through a optimization procedure we fitted the porosity and etching
rate corresponding to each current density.
We showed that an analysis of the data of just one of the samples, which we chose
as that with the largest current density range, yielded calibration
curves that allow the approximate prediction of the properties of the other
samples. The calibration curves can be used to design and calculate the optical
properties of other systems prepared under similar conditions, such as
multilayered GRIN systems from which photonic crystals, microcavities
and sensors with position dependent properties. This is the subject of
ongoing work. As the etching rate for the formation of porous silicon
and the resulting porosity are very sensitive to the growth conditions
and to the properties of the substrate, such as its doping,
there are no universal calibration curves. Thus, it is useful to have
a procedure that from just one sample can produce calibration curves
that may be employed for other samples grown in the same conditions.

>>>>

\section{Introduction}
\label{sec:introduction}
Surfaces with a gradient in the refractive index (GRIN) are of
importance as they allow the engineering and tuning of the optical
phase along their surface, yielding applications such as flat
lenses. Furtheremore, there are important biological applications
which combine topographical features with index of refraction
gradients \cite{pierscionek2012gradient}. Preparation of structures
with gradients in other properties have also shown their
usefulness. \notaL{I believe the examples below are unrelated to GRIN,
  thats why I added the previous remark.} As an example, the
roughness dependent  response of cells has been tested on
materials used applications in medical implants
\cite{bai2020bioinspired}.
Gradients have also been employed for several
technological applications such as high-yield screening of catalysts,
sensing materials and biomolecules \cite{maier2007combinatorial, jayaraman2004construction,
potyrailo2008combinatorial}
Apart from some methods developed by S.E. Fosdick et al \cite{fosdick2010two},
%[JACS  2010, 132, 9226-9227],
synthesis of  Ag-Au alloy gradients on steel and chemical composition
gradients of CdS layers
on gold electrodes have been obtained made by Shannon’s
group\cite{wang2019fabrication}. \notaL{Is this Shannon a big shot, or
  why should we name him?}
Among electrochemical methods, compositional and doping density changes
in  conducting polymers have been used to produce gradients using Indium Tin
Oxide electrodes \cite{inagi2010bipolar}
Electrochemically induced potential gradients have been shown to catalyze the
reactions and gradient doping of polymers \cite{qin2020bipolar, ishiguro2011gradient}.
As compared to the above mentioned techniques, a relatively economical,
fast and easy approach for the fabrication
of gradient materials has been the use  of asymmetrical
electrode configurations in the electrochemical synthesis of porous silicon \cite{sailor2012porous}.
This technique has the additional advantage of being compatible
with VLSI devices and integrable with microelectronics.

Although porous silicon (PS) initially stimulated the interest of the scientific
community due to its photoluminiscence in the visible range at room
temperature, it has presently
been recognized as a multifaceted optical material due to its large surface
area, biocompatibility, ease of fabrication and tunable refractive index.
Applications based on porous silicon now cover various fields such as
chemical sensors and biosensors \cite{kumar2020porous},
microelectronics and MEMS \cite{martinez2016dual},as well as a
range of optical \cite{estevez2014porous} and optoelectronic applications
\cite{ramadan2020fabrication}. Specifically,
the temporal variation of the current density results in a variation of
porosity along the depth, allowing the easy fabrication of different kinds
\cite{perez2018reflectivity} of 1D photonics crystals and other
structures. \notaL{Photonic crystals only in the periodic case.}
Although the conventional fabrication of PS yields laterally
homogeneous samples, with invariant structural and optical properties
along the surface, an asymmetric configuration \notaL{Is it clear what
  is asymmetric?} may produce porous
Silicon structures with a lateral gradient in properties such as
thickness, pore size and density, and thus, refractive index and
optical thickness. In this configuration, a small platinum electrode (cathode)
is positioned perpendicular  to the surface of a Si substrate (anode)
near one end \notaL{ At the center wouldn't be asymmetric: or the
  center} of the cell, resulting  in a current
density  which decreases as the distance to the electrode increases
 \cite{khung2008using, clements2011mesenchymal}.
The resulting porous surface can have pore sizes ranging from a few nanometers
to  few micrometers  \cite{wang2015screening}. The range of the dimensions of the pores and
the corresponding  thickness range on the same chip can be controlled by
adjusting the location of the electrode, the  anodizing current
and the etching time. Different
applications have been found for the resulting structures
\cite{collins2002determining}. For example, Sailor's group
\cite{collins2002determining, sailor2012porous} applied it
for the determination of protein size.
Additionally, gating of
the optical response through a variation in pH of the solution was shown to
trap/release biomolecules for possible drug delivery
applications, given the biocompatible nature of PS, . \notaL{How is this related to the gradient?}
A similar asymmetric electrode configuration was used to fabricate
multilayered optical filters with lateral a gradient
\cite{li2005painting} and
for developing ethanol sensors \cite{sailor2012porous}.
Additionally it has been shown that the combination of thermal  oxidation  and
infiltration of TiO2  by ALD \notaL{What is this acronym?} allows the manufacture
of transparent GRIN
optical elements with a high refractive index contrast \cite{ocier2017tunable}.
Kruger et al. showed the \cite{krueger2016porous} \notaL{What did
  Kruger show?}
Furthermore, the same group \cite{krueger2018electrochemical} used
a porous silicon 1D GRIN structure infiltrated with polymer to
synthesize flat microlens arrays.
Recently, J Wang et al. has shown the fabrication of
a miniature spectrometer with PS based rugate filter using a
radial interfacial potential distribution \cite{wang2019fabrication}
On the other hand, the effect of different topographical
features present on the same chip, has also been
used to study the dependence of the adhesion of certain cells on the
surface topography \cite{khung2008using}.

For applications such as those mentioned above,
it would be very useful to be able to predict beforehand the spatially dependent
properties of the resulting structures. This would allow the design
and optimization of the desired devices.
In this work, we report a simple analytical model to quantitatively
analyze the spatial dependence of the current density during the
electrochemical on Si to produce PS structures. A calibration
procedure may then relate the current density to the porosity and the
etching rate. Thus, for a given etching current acting over a given
time, we may predict the position dependence of the index of
refraction and optical thickness of the resulting inhomogeneous
layer, thus allowing the prediction of the optical properties of
multilayered GRIN structure. The structure of the paper is the
following.
\notaL{Check when finished}. In Section \ref{sec:theory} we develop a
simple analytical model to calculate
the current density at any point over the GRIN structure under preparaton.
In Section \ref{sec:procedures} we provide experimental details for the
synthesis of porous silicon samples with lateral refractive index gradient.
Section \ref{sec:discussion-results} includes experimental results and
its comparison with numerically evaluated parameters. Finally, we
devote Section \ref{sec:conclusions} to our concusions.

@@

This problem may be solved readily using image charge theory \cite{jackson1975classical}.

@@

\section{Conclusions}
\label{sec:conclusions}
By choosing a simple geometry for our electrochemical cell, namely, a
rectangular prism, and employing a point-like electrode, we were able
to derive an expression for the calculation of the electric current
density along the surface of a Si sample. The expression was obtained
by using image charge theory and a planewise summation of Coulomb
potentials in 2D reciprocal space, and it is made up of
a rapidly converging sum of analytical terms, just a few of which
should be kept. This allows the characterization
of the porosity of a PS layer and the etching
rate for different values of the etching current density by making
optical measurements on several positions of just a
few samples. We illustrated the procedure with three samples on each of which we
measured reflectance spectra at eight different positions.
Through a optimization procedure we fitted the porosity and etching
rate corresponding to each current density.
We showed that an analysis of the data of just one of the samples, which we chose
as that with the largest current density range, yielded calibration
curves that allow the approximate prediction of the properties of the other
samples. The calibration curves can be used to design and calculate the optical
properties of other systems prepared under similar conditions, such as
multilayered GRIN systems from which photonic crystals, microcavities
and sensors with position dependent properties. This is the subject of
ongoing work. As the etching rate for the formation of porous silicon
and the resulting porosity are very sensitive to the growth conditions
and to the properties of the substrate, such as its doping,
there are no universal calibration curves. Thus, it is useful to have
a procedure that from just one sample can produce calibration curves
that may be employed for other samples grown in the same conditions.
